A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-16 mt-marathon.2013/PBML_article.tex
changes

Even though each decoder was created independently, their output are comparable. We see that be doing an indepth analysis of the working of each decoder and comparing their model score, we are able to transfer the best optmization technique from each decoder to the others.

>>>>

Even though each decoder was created independently, their output are comparable. We see that by doing an indepth analysis of the working of each decoder and comparing their model scores, we are able to transfer the best optmization techniques from each decoder to the others.
